\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\title{Hazard Analysis\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle
\thispagestyle{empty}

~\newpage

\pagenumbering{roman}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
October 12 2022 & Darren & Added System Boundaries \& Components\\
Date2 & Name(s) & Description of changes\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

~\newpage

\tableofcontents

~\newpage

\pagenumbering{arabic}

\wss{You are free to modify this template.}

\section{Introduction}

This document is a hazard analysis of MTOBridge. A hazard is a potentially harmful event resulting
from the conditions of the system and the environment.

\section{Scope and Purpose of Hazard Analysis}

This document describes the components of MTOBridge, the potential hazards associated with each, and 
any new functional requirements that can be derived from these hazards. This process is important to 
identify any potential issues with the system, and then design the system to eliminate the potential issues.

\section{System Boundaries and Components}

This hazard analysis addresses the system that consists of the following components:

\begin{enumerate}
	\item UI Component, for providing a graphic display to the user and visualizing MATLAB results
	\item Input Handler Component, for processing user inputs
	\item MATLAB Interaction Component, for calling scripts and supplying specified arguments to them
	\item MATLAB Engine Component, for performing bridge calculations
	\item File Manager Component, for reading inputs from files and saving results in various formats
\end{enumerate}

The system boundary includes these software components and any dependency files required for the application to operate. Although the MATLAB Engine Component is owned by the client and its exact contents verified independent of this project, this hazard analysis will address it due to being a crucial component of the system.

\section{Critical Assumptions}

We will be making the following assumptions about the system:
\begin{enumerate}
    \item The MATLAB Engine Component will take less than 1 second to perform bridge calculations. 
    This is because the equations that need to be solved have closed form solutions, and should be easy
    to compute.
    \item The MATLAB Engine Component will be correct. We are assuming this because we do not have control
    over the MATLAB scripts that will be running.
    \item The user of the system will have input (keyboard, mouse) and output (monitor/display) devices.
\end{enumerate}

\section{Failure Mode and Effect Analysis}

\wss{Include your FMEA table here}

\section{Safety and Security Requirements}

\wss{Newly discovered requirements.  These should also be added to the SRS.  (A
rationale design process how and why to fake it.)}

\section{Roadmap}

\wss{Which safety requirements will be implemented as part of the capstone timeline?
Which requirements will be implemented in the future?}

\end{document}